Radio Telescope Observations Of The April 8, 2024 Total Solar Eclipse At 1420MHz.

### 2025-03-06 sections/observations.tex
Removed mention of .csv file
Added an explenation of what normalization is

@@

\paragraph{The Theoretical Lightcurve}
Our comparison lightcurve is a theoretical lightcurve from the software Stellarium, a free open source planetarium capable of calculating the eclipse magnitude and eclipse percentage from our observing location.
Using the Stellarium API, we extracted the eclipse percentage at 1000 points in time, from shortly before first contact, to shortly after fourth contact.

@@

@@

Dr. Todd Abel and Shane Ayotte provided the light sensor data in the form of a .csv file, which we normalized to relative brightness.

>>>>

Normalization is the process by which the data of a graph is scaled by a constant such that the highest points are equal to 100, essentially making the data a percentage of its highest value.

@@

@@

We compared this livestream lightcurve to a theoretical lightcurve generated by the software \texttt{Stellarium}\cite{zotti_simulated_2020}, and were happy to see that the livestream and theoretical lightcurves overlap quite well.

@@

Dr. Todd Abel and Shane Ayotte provided the light sensor data, which we normalized to relative brightness.
